%% ------------------------------ Abstract ---------------------------------- %%
\begin{abstract}

File system is an important component of an operating system. It defines the way data is stored and retrieved. Its performance and efficiency affect overall operating system.

In this study, we design, implement, and validate a new file system built-on FUSE. The file system is a distributed file system with snapshot capability, which use MongoDB as storage backend. We introduce a patch-based new strategy to store snapshots. Further, we apply the rsync algorithm to enhance the efficiency of classic copy-on-write snapshot as well as the network performance. In addition, we studied the performance and the effect of some factors that affect the efficiency of rsync enhanced copy-on-write snapshot.

Test results indicate that the file system we proposed has performance comparable to the popular network file system NFS. Furthermore, it shows that the rsync enhanced copy-on-write snapshot system can boost the space efficiency of the snapshot system compared to classic copy-on-write snapshot system. 

\end{abstract}

%% ---------------------------- Copyright page ------------------------------ %%
%% Comment the next line if you don't want the copyright page included.
\makecopyrightpage

%% -------------------------------- Title page ------------------------------ %%
\maketitlepage

%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
 \centering To my Father Xiaohua Wang, and my Mother Bei Lu

 \centering To my teachers

 \centering To all who take time to read this thesis
\end{dedication}

%% -------------------------------- Biography ------------------------------- %%
\begin{biography}

    The author was born in 1988 in Hangzhou, Zhejiang, China. Inspired by his parents, both are professors in computer science, he becomes interested in science and engineering.

    In 2006, he got admitted to his dream school Zhejiang University and started his major in Electronic Engineering there. Zhejiang University is also where his parents, his grandmother, and his cousin used to study. He made a number of friends and never felt lonely when he was there.

    He came to NC State University 4 years later and finished his first master degree program in Operations Research in 2 years. After his first Master's degree, he started pursuing his second master degree in Computer Science.

\end{biography}

%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}
I would like to thank the following people:

\begin{itemize}
\item Dr. Vincent Freeh
\item Dr. Rada Chirkova
\item Dr. Emerson Murphy-Hill
\item Dr. Pual Mugge
\item Kamal Kc
\end{itemize}

\end{acknowledgements}


\thesistableofcontents

\thesislistoftables

\thesislistoffigures
